---
title: "classification_model"
output: html_document
date: "2023-06-16"
---

**Section 2 - Classification Approach**

```{r,include=FALSE}
pkg <- c('dplyr', 'scales', 'tidyr', 'ggplot2', 'data.table', 'readr', 
         'tidymodels', 'ranger', 'knitr', 'summarytools', 
         'tidyverse', 'recipes', 'stats', 'janitor','cluster','car','pheatmap','randomForest','Boruta')

check_and_install <- function(p) {
  if(!require(p, character.only = TRUE)) {
    install.packages(p, dependencies = TRUE)
    library(p, character.only = TRUE)
  }
}

sapply(pkg, check_and_install)

```

```{r,include=FALSE}
# Load the datasets
survey_data_classification <- read_csv("data/mxmh_survey_results.csv")
spotify_data_classification <- read_csv("data/spotify.csv")
```

**Clean features name - using janitor**

```{r,include=FALSE}
survey_data_classification <- survey_data_classification %>%
  clean_names()
survey_data_classification <- rename(survey_data_classification, frequency_r_n_b = frequency_r_b)
survey_data_classification <- select(survey_data_classification, -c(frequency_video_game_music, frequency_rap, frequency_lofi))
```

**Calculate attribute scores to each genre**

```{r,include=FALSE}
# Define the genres of interest
genres_of_interest <- c("classical", "country", "edm", "folk", "gospel", "hip_hop", 
                        "jazz", "k_pop", "latin", "metal", "pop", "r_n_b", "rock")
features <- c("danceability", "energy",  "loudness", "speechiness",
              "acousticness", "instrumentalness", "liveness", "valence", "tempo")

# Filter spotify_data_classification for the genres of interest
spotify_data_classification <- spotify_data_classification %>%
  filter(track_genre %in% genres_of_interest)


# Calculate mean for each genre in filtered_spotify_data_classification
spotify_means <- spotify_data_classification %>%
  group_by(track_genre) %>%
  summarise(across(features, mean, na.rm = TRUE), .groups = 'drop')

# Define the genre columns in survey_data
genre_cols <- c("weight_classical", "weight_country", "weight_edm", "weight_folk", "weight_gospel",
                "weight_hip_hop", "weight_jazz", "weight_k_pop", "weight_latin", "weight_metal",
                "weight_pop", "weight_r_n_b", "weight_rock")

spotify_means <- spotify_means %>%
  mutate(track_genre = paste0("frequency_", track_genre))
specific_genres <- c("classical", "country", "edm", "folk", "gospel", "hip_hop", "jazz", "k_pop", "latin", "metal", "pop", "r_n_b", "rock")
# Create a list of genre columns in survey_data
genre_cols <- paste0("frequency_", specific_genres)

freq_map <- c("Never" = 0, "Rarely" = 0.33, "Sometimes" = 0.67, "Very frequently" = 1)

survey_data_classification <- survey_data_classification %>%
  mutate(across(starts_with("frequency_"), ~ freq_map[.])) 

features <- c("danceability", "energy",  "loudness", "speechiness", "acousticness", "instrumentalness", "liveness", "valence","tempo")


```

```{r,include=FALSE}
for (i in 1:nrow(survey_data_classification)) {
  # Initialize variables
  multi <- rep(0, length(features))
  division <- 0
  for (feature in features) {
    multi <- rep(0, length(features))
    division <- 0
    for (genre_col in genre_cols) {
      weight <- as.numeric(survey_data_classification[i, genre_col])* as.numeric(survey_data_classification[i, "hours_per_day"])
      weights <- rep(weight, length(features))
      
      # Get genre means for the current genre and feature
      genre_means <- as.numeric(unlist(spotify_means[spotify_means$track_genre == genre_col, feature]))

      # Skip iteration if genre_means is empty
      if (length(genre_means) == 0)
        next
      
      # Multiply weight with each feature value and accumulate the sum
      multi <- multi + (weights * genre_means)
      
      # Accumulate the weight in the division variable
      division <- division + weight
    }
      # Create a vector of the same length as features, filled with the division value
  divisions <- rep(division, length(features))
  
  # Calculate the weighted average
  weighted_average <- ifelse(division == 0, 0, multi / divisions)
  
  # Add the weighted average to the survey_data
  survey_data_classification[i, paste0(feature,"_score")] <- weighted_average
  }
}
```

**We will calculate the spearman corrolation between each score to each one of the mental health oridinally features**

```{r}
# Assuming your data frame is named survey_data_classification
X_variables <- c('danceability_score', 'energy_score', 'loudness_score', 
                 'speechiness_score', 'acousticness_score', 'instrumentalness_score',
                 'liveness_score', 'valence_score', 'tempo_score')

Y_variables <- c("ocd", "depression", "insomnia", "anxiety")

# Initialize an empty data frame to store the correlation results
correlation_results <- data.frame()

# Calculate Spearman's rank correlation
for (x in X_variables) {
  for (y in Y_variables) {
    correlation <- cor.test(survey_data_classification[[x]], survey_data_classification[[y]], method = "spearman")
    result <- data.frame(
      X_variable = x,
      Y_variable = y,
      correlation = correlation$estimate,
      p_value = correlation$p.value
    )
    correlation_results <- rbind(correlation_results, result)
  }
}

# Filter the results
filtered_results <- correlation_results %>%
  filter(p_value < 0.05)

# Print the filtered results
print(filtered_results)

```

**We can see that some of the music scores have correlation only with depression, we will focus on depression.**

```{r}
# set.seed(123)
# 
# clustering_function <- function(data, column, k) {
#   # Prepare the data
#   target_data <- data[[column]]
#   
#   # Perform k-means clustering
#   kmeans_result <- kmeans(target_data, centers = k)
#   
#   # Determine the cut points
#   breaks <- quantile(target_data, probs = seq(0, 1, length.out = k + 1))
#   categories <- cut(target_data, breaks = breaks, labels = c("1", "2", "3"))
#   
#   # Print the ranges for each cluster
#   for (i in 1:k) {
#     range_start <- breaks[i]
#     range_end <- breaks[i+1]
#     cluster_label <- levels(categories)[i]
#     cat("Cluster", i, ":", cluster_label, "(", range_start, "-", range_end, ")\n")
#   }
#   
#   return(categories)
# }
# 
# # Usage
# depression_categories <- clustering_function(survey_data_classification, "depression", 3)
# insomnia_categories <- clustering_function(survey_data_classification, "insomnia", 3)
# anxiety_categories <- clustering_function(survey_data_classification, "anxiety", 3)



```

## We will split the data to see if the corellation will improve\*\*

```{r,include=FALSE}
# Creating the "low" tibble
low_depression <- survey_data_classification %>% filter(depression <= 3)

# Creating the "medium" tibble
medium_depression <- survey_data_classification %>% filter(depression > 3 & depression <= 7)

# Creating the "high" tibble
high_depression <- survey_data_classification %>% filter(depression > 7)

# Creating the "low" tibble
low_insomnia <- survey_data_classification %>% filter(insomnia <= 3)

# Creating the "medium" tibble
medium_insomnia <- survey_data_classification %>% filter(insomnia > 3 & insomnia <= 7)

# Creating the "high" tibble
high_insomnia <- survey_data_classification %>% filter(insomnia > 7)

# Creating the "low" tibble
low_anxiety <- survey_data_classification %>% filter(anxiety <= 3)

# Creating the "medium" tibble
medium_anxiety <- survey_data_classification %>% filter(anxiety > 3 & anxiety <= 7)

# Creating the "high" tibble
high_anxiety <- survey_data_classification %>% filter(anxiety > 7)

# Creating the "low" tibble
low_ocd <- survey_data_classification %>% filter(ocd <= 3)

# Creating the "medium" tibble
medium_ocd <- survey_data_classification %>% filter(ocd > 3 & anxiety <= 7)

# Creating the "high" tibble
high_ocd <- survey_data_classification %>% filter(ocd > 7)

```

```{r}
# List of features
features_score <- c("danceability_score", "energy_score",  "loudness_score", "speechiness_score", "acousticness_score", "instrumentalness_score", "liveness_score", "valence_score", "tempo_score")

# Empty dataframe to store results
correlation_df <- data.frame()

# List of dataframes
dataframes <- list(low_depression = low_depression, 
                   medium_depression = medium_depression, 
                   high_depression = high_depression,
                   low_insomnia = low_insomnia, 
                   medium_insomnia = medium_insomnia, 
                   high_insomnia = high_insomnia, 
                   low_anxiety = low_anxiety, 
                   medium_anxiety = medium_anxiety, 
                   high_anxiety = high_anxiety,
                   low_ocd = low_ocd, 
                   medium_ocd = medium_ocd, 
                   high_ocd = high_ocd)

# Loop through each dataframe
for (df_name in names(dataframes)) {
  
  # Extract condition from table name
  condition <- strsplit(df_name, "_")[[1]][2]
  
  # Loop through each feature
  for (feature in features_score) {
    
    # Perform Spearman correlation test
    result <- cor.test(dataframes[[df_name]][[feature]], dataframes[[df_name]][[condition]], method = "spearman")

    # Check if p-value is less than 0.05
    if (result$p.value < 0.05) {
      
      # If p-value is less than 0.05, add result to correlation_df
      correlation_df <- rbind(correlation_df, data.frame(TableName = df_name, Feature = feature, Correlation = result$estimate, P_Value = result$p.value))
    }
  }
}

# Print the correlation_df dataframe
print(correlation_df)


```


```{r}
# Split the data into training and testing datasets
set.seed(123)
data_split <- initial_split(survey_data_classification, prop = 0.8)
train_data <- training(data_split)
test_data <- testing(data_split)
```

**Now, lets split each mental health feature to categories and factor it**

```{r}

train_data <- train_data %>%
  mutate(
    depression = as.factor(ifelse(depression > 7, 3, ifelse(depression > 3, 2, 1))),
    ocd = as.factor(ifelse(ocd >= 7, 3, ifelse(ocd >= 3, 2, 1))),
    insomnia = as.factor(ifelse(insomnia >= 5, 3, ifelse(insomnia > 2, 2, 1))),
    anxiety = as.factor(ifelse(anxiety > 7, 3, ifelse(anxiety >5, 2, 1)))
  )

test_data <- test_data %>%
  mutate(
    depression = as.factor(ifelse(depression > 7, 3, ifelse(depression > 3, 2, 1))),
    ocd = as.factor(ifelse(ocd >= 7, 3, ifelse(ocd >= 3, 2, 1))),
    insomnia = as.factor(ifelse(insomnia >= 5, 3, ifelse(insomnia > 2, 2, 1))),
    anxiety = as.factor(ifelse(anxiety > 7, 3, ifelse(anxiety >5, 2, 1)))
  )
```

**Use chisq for feature selection. we show the features we want to remove from the model**

```{r}

# list all the categorical variables
categorical_vars <- c("primary_streaming_service", "while_working", "instrumentalist", "composer", "fav_genre", "exploratory", "foreign_languages", 
                      "frequency_classical", "frequency_country", "frequency_edm", "frequency_folk", "frequency_gospel", 
                      "frequency_hip_hop", "frequency_jazz", "frequency_k_pop", "frequency_latin", "frequency_metal", 
                      "frequency_pop", "frequency_r_n_b", "frequency_rock")

# initialize an empty vector to store p-values
p_values <- c()

# loop over each categorical variable
for (var in categorical_vars) {

  # perform chi-square test
  chi_test <- chisq.test(train_data[[var]], train_data$depression)
  # store the p-value
  p_values <- c(p_values, chi_test$p.value)
}

# create a data frame to view variable names and their corresponding p-values
chi_results <- data.frame(Variables = categorical_vars, P_Value = p_values)

# Check which features' p_value are greater than 0.05 (the alpha)
chi_results_filtered <- chi_results %>% filter(P_Value > 0.05)

chi_results_filtered
```

```{r}
set.seed(123)

# Define a function to run the model
run_model <- function(train_data, test_data, target_variable, rec) {
  # Specify the model to use
  model_spec <- 
    rand_forest(trees = 1000, min_n = tune()) %>%
    set_engine("ranger", importance = 'impurity') %>%
    set_mode("classification")

  # Combine the model and recipe into a workflow
  workflow <- 
    workflow() %>%
    add_recipe(rec) %>%
    add_model(model_spec)

  # Define a cross-validation plan
  cv <- vfold_cv(train_data, v = 5, strata = target_variable)

  # Tune the model
  tuned_wf <- tune_grid(
    workflow,
    resamples = cv,
    grid = 10,
    control = control_grid(verbose = FALSE)
  )

  # Extract the best parameters
  best_params <- tuned_wf %>% select_best("accuracy")

  # Update the workflow with the best parameters
  final_wf <- workflow %>% finalize_workflow(best_params)

  # Fit the final workflow on the training data
  final_fit <- final_wf %>% fit(train_data)

  # Apply to the testing data
  results <- final_fit %>%
    predict(test_data) %>%
    bind_cols(test_data[target_variable])

  return(results)
}
```

**Run the classification model to predict depression level**

```{r}
rec_depression <- recipe(depression ~ ., data = train_data) %>%
  step_impute_mode(instrumentalist,while_working,music_effects,foreign_languages,primary_streaming_service,fav_genre ) %>%
  step_impute_median(age,bpm) %>%
  step_rm(timestamp, permissions, anxiety, ocd, insomnia, while_working, instrumentalist, composer,
          exploratory, frequency_classical,frequency_folk, frequency_gospel, frequency_jazz, frequency_k_pop,
          frequency_pop, frequency_country, primary_streaming_service, frequency_r_n_b,
          "loudness_score", "speechiness_score", "liveness_score",
          "valence_score", "instrumentalness_score","danceability_score") %>%
  step_mutate(music_effects = as.factor(ifelse(music_effects %in% c("Worsen", "Improve"), 1, 0))) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_zv(all_predictors())
# Run the model for depression
depression_results <- run_model(train_data, test_data, "depression", rec_depression)

cm <- conf_mat(depression_results, truth = depression, estimate = .pred_class)
f1_score <- f_meas(depression_results, truth = depression, estimate = .pred_class)
precision_score <- precision(depression_results, truth = depression, estimate = .pred_class)
recall_score <- recall(depression_results, truth = depression, estimate = .pred_class)
accuracy_score <- accuracy(depression_results, truth = depression, estimate = .pred_class)

print(cm)

cat("\n\nF1 Score: ", f1_score$.estimate, "\n")
cat("Precision: ", precision_score$.estimate, "\n")
cat("Recall: ", recall_score$.estimate, "\n")
cat("Accuracy: ", accuracy_score$.estimate, "\n")
```

**Run the classification model to predict insomnia level**

```{r}
rec_insomnia <- recipe(insomnia ~ ., data = train_data) %>%
  step_impute_mode(instrumentalist,while_working,music_effects,foreign_languages,primary_streaming_service,fav_genre ) %>%
  step_impute_median(age,bpm) %>%
  step_rm(timestamp, permissions, anxiety, ocd, depression, while_working, instrumentalist, composer,
          exploratory, frequency_classical,frequency_folk, frequency_gospel, frequency_jazz, frequency_k_pop,
          frequency_pop, frequency_country, primary_streaming_service, frequency_r_n_b,"speechiness_score", "liveness_score","valence_score", "danceability_score") %>%
  step_mutate(music_effects = as.factor(ifelse(music_effects %in% c("Worsen", "Improve"), 1, 0))) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_zv(all_predictors())
# Run the model for depression
insomnia_results <- run_model(train_data, test_data, "insomnia", rec_insomnia)

cm <- conf_mat(insomnia_results, truth = insomnia, estimate = .pred_class)
f1_score <- f_meas(insomnia_results, truth = insomnia, estimate = .pred_class)
precision_score <- precision(insomnia_results, truth = insomnia, estimate = .pred_class)
recall_score <- recall(insomnia_results, truth = insomnia, estimate = .pred_class)
accuracy_score <- accuracy(insomnia_results, truth = insomnia, estimate = .pred_class)

print(cm)

cat("\n\nF1 Score: ", f1_score$.estimate, "\n")
cat("Precision: ", precision_score$.estimate, "\n")
cat("Recall: ", recall_score$.estimate, "\n")
cat("Accuracy: ", accuracy_score$.estimate, "\n")
```

**Run the classification model to predict anxiety level**

```{r}
rec_anxiety <- recipe(anxiety ~ ., data = train_data) %>%
  step_impute_mode(instrumentalist,while_working,music_effects,foreign_languages,primary_streaming_service,fav_genre ) %>%
  step_impute_median(age,bpm) %>%
  step_rm(timestamp, permissions, ocd, insomnia, depression, while_working, instrumentalist, composer,
          exploratory, frequency_classical,frequency_folk, frequency_gospel, frequency_jazz, frequency_k_pop,
          frequency_pop, frequency_country, primary_streaming_service, frequency_r_n_b,"loudness_score", "liveness_score",
          "valence_score", "instrumentalness_score","danceability_score") %>%
  step_mutate(music_effects = as.factor(ifelse(music_effects %in% c("Worsen", "Improve"), 1, 0))) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_zv(all_predictors())
# Run the model for depression
anxiety_results <- run_model(train_data, test_data, "anxiety", rec_anxiety)

cm <- conf_mat(anxiety_results, truth = anxiety, estimate = .pred_class)
f1_score <- f_meas(anxiety_results, truth = anxiety, estimate = .pred_class)
precision_score <- precision(anxiety_results, truth = anxiety, estimate = .pred_class)
recall_score <- recall(anxiety_results, truth = anxiety, estimate = .pred_class)
accuracy_score <- accuracy(anxiety_results, truth = anxiety, estimate = .pred_class)

print(cm)

cat("\n\nF1 Score: ", f1_score$.estimate, "\n")
cat("Precision: ", precision_score$.estimate, "\n")
cat("Recall: ", recall_score$.estimate, "\n")
cat("Accuracy: ", accuracy_score$.estimate, "\n")
```

**Run the classification model to predict OCD level**

```{r}
rec_ocd <- recipe(ocd ~ ., data = train_data) %>%
  step_impute_mode(instrumentalist,while_working,music_effects,foreign_languages,primary_streaming_service,fav_genre ) %>%
  step_impute_median(age,bpm) %>%
  step_rm(timestamp, permissions, anxiety, insomnia, depression, while_working, instrumentalist, composer,
          exploratory, frequency_classical,frequency_folk, frequency_gospel, frequency_jazz, frequency_k_pop,
          frequency_pop, frequency_country, primary_streaming_service, frequency_r_n_b,"loudness_score", "liveness_score",
          "valence_score", "instrumentalness_score","danceability_score") %>%
  step_mutate(music_effects = as.factor(ifelse(music_effects %in% c("Worsen", "Improve"), 1, 0))) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_zv(all_predictors())
# Run the model for depression
ocd_results <- run_model(train_data, test_data, "ocd", rec_ocd)

cm <- conf_mat(ocd_results, truth = ocd, estimate = .pred_class)
f1_score <- f_meas(ocd_results, truth = ocd, estimate = .pred_class)
precision_score <- precision(ocd_results, truth = ocd, estimate = .pred_class)
recall_score <- recall(ocd_results, truth = ocd, estimate = .pred_class)
accuracy_score <- accuracy(ocd_results, truth = ocd, estimate = .pred_class)

print(cm)

cat("\n\nF1 Score: ", f1_score$.estimate, "\n")
cat("Precision: ", precision_score$.estimate, "\n")
cat("Recall: ", recall_score$.estimate, "\n")
cat("Accuracy: ", accuracy_score$.estimate, "\n")
```

## getting insights on each category group for depression

```{r}
cleaned_data <- na.omit(survey_data_classification)

# Creating the "low" tibble
low_depression <- cleaned_data %>% filter(depression <= 3)

# Creating the "medium" tibble
medium_depression <- cleaned_data %>% filter(depression >= 4 & depression <= 7)

# Creating the "high" tibble
high_depression <- cleaned_data %>% filter(depression >= 8)
```


```{r}
test_variance <- function(group1, group2) {
  combined_data <- bind_rows(
    group1 %>% mutate(group = 'group1'),
    group2 %>% mutate(group = 'group2')) %>%
    select(-one_of("depression", "anxiety", "ocd", "insomnia"))
  
  # List to store ANOVA results
  anova_results <- list()
  
  # Iterate over each numerical variable
  numerical_variables <- colnames(combined_data)[sapply(combined_data, is.numeric)]
  for (var in numerical_variables) {
    formula <- as.formula(paste(var, " ~ group"))
    anova_results[[var]] <- aov(formula, data = combined_data)
  }
  
  # Print ANOVA results
  for (var in numerical_variables) {
    print(var)
    print(summary(anova_results[[var]]))
  }
}

```

**variance test between "low_depression" and "medium_depression"**

```{r}
test_variance(low_depression, medium_depression)
```

**variance test between "medium_depression" and "high_depression"**

```{r}
test_variance(medium_depression, high_depression)

```



**variance test between "low_depression" and "high_depression"**

```{r}
test_variance(low_depression, high_depression)
```

**Now we will test another approach**

```{r}
# Split the data into training and testing datasets
set.seed(123)
data_split <- initial_split(survey_data_classification, prop = 0.8)
train_data <- training(data_split)
test_data <- testing(data_split)
```

**Create a new binary feature which is 1 if the sum of exp of ocd,anxiety,insomnia,depression is greater than e\^6,otherwise 0**

```{r}
train_data <- train_data %>%
  mutate(
    mental_health = as.factor(ifelse((exp(ocd) + exp(anxiety) + exp(insomnia) + exp(depression)) >= 2 * exp(6), 1, 0))
  )

test_data <- test_data %>%
  mutate(
    mental_health = as.factor(ifelse((exp(ocd) + exp(anxiety) + exp(insomnia) + exp(depression)) >= 2 * exp(6), 1, 0))
  )
```

**Feture Selection using boruta algorithm**

```{r}
data <- train_data
data <- data[, !(names(data) %in% c("anxiety", "depression", "insomnia", "ocd"))]

data <- na.omit(data)

categorical_features <- c('primary_streaming_service', 'while_working', 'instrumentalist', 'composer', 'fav_genre', 'exploratory', 'foreign_languages')

for(col in categorical_features){
  data[[col]] <- as.factor(data[[col]])
}
X <- data[, -which(names(data) %in% "mental_health")]
y <- as.factor(data$mental_health)  # convert target to factor
set.seed(123)  # for reproducibility

# Apply Boruta feature selection method
boruta_output <- Boruta(X, y, doTrace=2)  # doTrace=2 for some logs to see progress

# Handle the tentative variables
boruta_output <- TentativeRoughFix(boruta_output)

# Get finalized important variables
final_vars <- getSelectedAttributes(boruta_output, withTentative = F)

print(final_vars)
```

```{r}
set.seed(123)

# Define a function to run the model
run_model <- function(train_data, test_data, target_variable, rec) {
  # Specify the model to use
  model_spec <- 
    rand_forest(trees = 1000, min_n = tune()) %>%
    set_engine("ranger", importance = 'impurity') %>%
    set_mode("classification")

  # Combine the model and recipe into a workflow
  workflow <- 
    workflow() %>%
    add_recipe(rec) %>%
    add_model(model_spec)

  # Define a cross-validation plan
  cv <- vfold_cv(train_data, v = 5, strata = target_variable)

  # Tune the model
  tuned_wf <- tune_grid(
    workflow,
    resamples = cv,
    grid = 10,
    control = control_grid(verbose = FALSE)
  )

  # Extract the best parameters
  best_params <- tuned_wf %>% select_best("accuracy")

  # Update the workflow with the best parameters
  final_wf <- workflow %>% finalize_workflow(best_params)

  # Fit the final workflow on the training data
  final_fit <- final_wf %>% fit(train_data)

  # Apply to the testing data
  results <- final_fit %>%
    predict(test_data) %>%
    bind_cols(test_data[target_variable])

  return(results)
}


```

**Run Overall mental helath clasffication method**

```{r}

rec_mental_health <- recipe(mental_health ~ age+hours_per_day+frequency_rock+danceability_score+energy_score+loudness_score+acousticness_score+instrumentalness_score+tempo_score, data = train_data) %>%
  step_impute_median(age,hours_per_day) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_zv(all_predictors())

mental_health_results <- run_model(train_data, test_data, "mental_health", rec_mental_health)

mental_health_results <- mental_health_results %>%
  mutate(mental_health = factor(mental_health, levels=c(1,0))) %>%
  mutate(.pred_class = factor(.pred_class, levels=c(1,0)))

cm <- conf_mat(mental_health_results, truth = mental_health, estimate = .pred_class)
f1_score <- f_meas(mental_health_results, truth = mental_health, estimate = .pred_class)
precision_score <- precision(mental_health_results, truth = mental_health, estimate = .pred_class)
recall_score <- recall(mental_health_results, truth = mental_health, estimate = .pred_class)
accuracy_score <- accuracy(mental_health_results, truth = mental_health, estimate = .pred_class)

print(cm)

cat("\n\nF1 Score: ", f1_score$.estimate, "\n")
cat("Precision: ", precision_score$.estimate, "\n")
cat("Recall: ", recall_score$.estimate, "\n")
cat("Accuracy: ", accuracy_score$.estimate, "\n")
```
